Spin canonical divisors of log stacky curves

### 2015-06-20 stacky_write_up/spin_cring.tex
editing section 3

\newcommand \subhalf[1]{\frac{{#1} - 1}{2{#1}}}
\newcommand{\se}[1]{\section*{Problem #1}}

@@

\section{Effective Genus Zero Spin Divisors}
\label{sec:g_0_effective}
Let us consider $\delta \geq 2$.

>>>>

\newcommand \subhalf[1]{\frac{{#1} - 1}{2{#1}}}
\newcommand{\se}[1]{\section*{Problem #1}}
\newcommand \halfcan{L}

@@

\section{Effective Genus Zero Spin Divisors}
\label{sec:g_0_effective}
In this section, we examine the case $2\halfcan\sim K_\sx+\Delta$ when $\Delta$ is a non-zero effective divisor.  Using this, we can reduce to looking at effective stacky divisors.  Then, applying a result for general effective $\mathbf{Q}$ divisors, we deduce that $R_{\halfcan}$ is generated in degrees up to $e=\max{e_i}$ with relations generated up to degree $2e$ with initial terms quadratic in the generators.  We also demonstrate that these bounds are tight up to \todo{insert how tight they are}.

Then we find $2\halfcan=D+\sum \subhalf{i}P_i$ where $D\sim K_X+\Delta\sim -2\infty+\Delta$ is a divisor of $X$ (i.e. with possibly negative integer coefficients). 
 Since $\Delta$ is non-zero effective, $\deg(D)\ge -1$.  
 Noting that the coefficient of any point $P$ occurring in a stacky divisor of $\sx$ must have coefficient lying in $\mathbf{Z}[\frac{1}{e_i}]$ (ranging over $e_i$s appearing in the characteristic of $(\sx,\Delta)$).  
Since all $e_i$s are odd, $2$ cannot appear in a denominator of the coefficient of a point $P$ in $\halfcan$, meaning that $\frac{D}{2}$ must be a $X$-divisor.  
Since $\deg(\frac{D}{2})=\frac{1}{2}\deg(D)\ge -\frac{1}{2}$, we in fact have $\deg(D)\ge 0$.  
Thus $\halfcan$ is linearly equivalent to an effective $X$ divisor plus $\sum \subhalf{i}P_i$.  
We have now reduced to the case of $\halfcan$ linearly equivalent to an effective divisor.  The result in this specific case in fact generalizes to any $\mathbf{Q}$-divisor: $\sum \frac{\alpha_i}{\beta_i} P_i$ for $\alpha_i,\beta_i\in \mathbf{N}$.

To prove thisUsing induction, we can prove prove that $\halfcan$ is generated up to degrees $e$ with relations up to degree $2e$.  O'Dorney \todo{Insert reference} proves
